251 MA

### 2022-11-20 code/process.Rmd
work to auto get pvals

---
title: "Preliminary stuff"
output: html_document
date: "2022-10-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
theme_set(theme_bw())
```

# TODOs
 - Fill in ES conversion for non d/SMD/partial eta (and check for correct conversion of those)

@@

```{r}
d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=2) |> 
  select(target_lastauthor_year, status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_pvalue, target_ES_type, target_ES_value,
         replication_N, replication_test, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code)

@@

```{r}
d |> group_by(status) |> tally()
```

>>>>

---
title: "251 MA"
output:
  html_document: 
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
theme_set(theme_bw())
```

# TODOs
- get ES from t test, from F test (using compute es) < -- what does within_one and within_two mean??
- validate df against num people?
- what about for other test statistics

@@

```{r}
d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=2) |> 
  select(target_lastauthor_year, status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, target_ES_value,
         replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code)

@@

```{r}
d |> group_by(status) |> tally()
```
# Validation

```{r}
d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))

d_val$academic_year |> unique()

d_val |> filter(!subfield %in% c("social","cognitive","non-psych","other-psych"))

d_val |> filter(!stanford_internal %in% c("no","yes"))

d_val |> filter(!open_data %in% c("no","yes"))

d_val |> filter(!open_materials %in% c("no","yes"))

d_val |> filter(!target_on_turk %in% c("no","yes"))

d_val |> filter(!replication_on_turk %in% c("no","yes"))

d_val |> filter(!within_between %in% c("within","between","mixed"))

d_val |> filter(!single_vignette %in% c(0,1))

```
# Parsing
```{r}
test <- "t(42)=2.41"
ftest <- "F(1,12)=45.43"
parse_t <- function(tval) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  return(data.frame("df_2"=df,"tstat"=val))
}

parse_f <- function(fval){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  return(data.frame("df_1"=df_1,"df_2"=df_2,"fstat"=val))
}

p_from_t <- function(d) {
  pt(q=d$tstat, df=d$df_2, lower.tail=FALSE)*2 # two tailed
}

p_from_f <- function(d) {
  pf(q=d$fstat, df1=d$df_1, df2=d$df_2, lower.tail=FALSE)
}

parse_t(test) |> p_from_t()
parse_f(ftest) |> p_from_f()

```{r}
test <-  d_val |> 
  mutate(target_p_calc=case_when(
    str_sub(target_raw_stat,1,1)=="t" ~ parse_t(target_raw_stat) |> p_from_t(),
    str_sub(target_raw_stat,1,1)=="F" ~ parse_f(target_raw_stat) |> p_from_f()),
    rep_p_calc=case_when(
    str_sub(replication_raw_stat,1,1)=="t" ~parse_t(replication_raw_stat) %>% p_from_t(),
    str_sub(replication_raw_stat,1,1)=="F" ~parse_f(replication_raw_stat) |> p_from_f()))

ggplot(test, aes(x=target_pvalue, y=target_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+
  scale_x_log10()+scale_y_log10()

ggplot(test, aes(x=replication_pvalue, y=rep_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+scale_x_log10()+scale_y_log10()
